Data Prep

### 2024-01-19 00.0_dataPrep.qmd
moved the low fix rate removal earlier in the process

-   `data/``dataPrep``/ornitela.feather`

@@

-   `data/``dataPrep``/joined.feather`

@@

-   `data/``dataPrep``/removed_periods.feather`

@@

-   `data/``dataPrep``/roosts0.Rda`

-   `data/``dataPrep``/removed_captures.feather`

@@

-   `data/``dataPrep``/seasons_list.Rda`

-   `data/``dataPrep``/season_names.Rda`

@@

@@

```{r}
load("data/dataPrep/seasons_list.Rda")
```

```{r}
#| eval: false
# Get roosts for each season ----------------------------------------------
roosts <- purrr::map(seasons_list, ~vultureUtils::get_roosts_df(df = .x, id = "Nili_id"))
roosts <- roosts %>%
  map(., ~st_as_sf(.x, crs = "WGS84", 
                   coords = c("location_long", "location_lat"), 
                   remove = F))
save(roosts, file = "data/dataPrep/roosts.Rda")

# Tidy up
rm(seasons_list)
rm(roosts)
gc()
```

@@

```{r}
removed_lfr <- map2(seasons_list, low_fix_rate_indivs,
                    ~.x %>% filter(!(Nili_id %in% .y)))
save(removed_lfr, file = "data/dataPrep/removed_lfr.Rda")

# tidy up
rm(seasons_list)
rm(low_fix_rate_indivs)
rm(removed_lfr)
gc()
```

>>>>

@@

@@

-   `data/dataPrep/removed_periods.feather`

@@

-   `data/dataPrep/roosts0.Rda`

@@

@@

```{r}
removed_lfr <- map2(seasons_list, low_fix_rate_indivs,                     ~.x %>% filter(!(Nili_id %in% .y))) 
save(removed_lfr, file = "data/dataPrep/removed_lfr.Rda")  
# tidy up 
rm(seasons_list) 
rm(low_fix_rate_indivs) 
rm(removed_lfr) 
gc()
```

@@

```{r}
load("data/dataPrep/removed_lfr.Rda")
```

```{r}
#| eval: false
# Get roosts for each season ----------------------------------------------
roosts <- purrr::map(removed_lfr, ~vultureUtils::get_roosts_df(df = .x, id = "Nili_id"))
roosts <- roosts %>%
  map(., ~st_as_sf(.x, crs = "WGS84", 
                   coords = c("location_long", "location_lat"), 
                   remove = F))
save(roosts, file = "data/dataPrep/roosts.Rda")

# Tidy up
rm(removed_lfr)
rm(roosts)
gc()
```

@@
